Meaningful data sharing

### 2020-09-22 new-paper.Rmd
working on avenues

(**note: on what to say**)
1. Data should go into Domain area - e.g., gbif for species data, or genbif or genbank for genetics data @GenBank. More information can be found at https://www.nature.com/sdata/policies/repositories. Importantly, domain areas should provide some form of accession number.

As discussed in \@ref(cite), archive data using a platform generating an accession number such as a DOI. For sharing data collected for research, the most relevant homes for general data are the research data repositories **zenodo** and **dryad**. In addition to minting DOIs, they also provide citation templates that can be used in \@ref(cite).

>>>>

(**note: still need to work on this**)

Data should be deposited into a relevant domain repository. For example, gbif [@gbif] for species data, or genbif or genbank for genetics data @GenBank. Information on other domain specific repositories can be found at https://www.nature.com/sdata/policies/repositories.

As discussed in \@ref(cite), archive data using a platform generating an accession number such as a DOI. For sharing data collected for research, the most relevant homes for general data are the research data repositories **zenodo** and **dryad**. In addition to minting DOIs, they also provide citation templates.
